% --- LaTeX CV Template - S. Venkatraman ---

% Set document class and font size
\documentclass[letterpaper, 11pt]{article}
% \usepackage[utf8]{inputenc}

% Package imports
\usepackage{longtable, graphicx, hyperref, fancyhdr, bookman}

% --- Page layout settings ---

% Set page margins
\usepackage[left=0.65in, right=0.65in, bottom=1.2in, top=1in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.15}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}

% Remove page numbering
% \pagenumbering{gobble}

% --- Document starts here ---

\begin{document}

% Name and date of last update to this document
\noindent{\,\ \ \ \Huge{CHANG Yung-Hsuan}
\hfill{\it\footnotesize Updated on \today\ \ \,\!}
}

% --- Contact information and other items ---

\vspace{0.5cm}
\noindent\:\ \ \ 
\textbf{Email}: \href{mailto:eiken0525@gmail.com}{eiken0525@gmail.com} 
\qquad \ \ 
\href{https://www.linkedin.com/in/eiken59}{\textbf{LinkedIn}} 
\qquad \ \ 
\href{https://eiken59.github.io}{\textbf{Website}}
\hfill 
\textit{\footnotesize Latest version: \href{https://github.com/eiken59/CV/blob/main/eiken59_CV.pdf}{my GitHub}\ \ \ \ }
\vspace{0.2cm}

% --- Start the two-column table storing the main content ---

% Set spacing between columns
\setlength{\tabcolsep}{8pt}
\vspace{-1.5em}
% Set the width of each column
\begin{center}
    \begin{longtable}{p{0.76in}p{5.93in}}

        % --- Section: Research interests ---
        
        % \nohyphens{\color{OliveGreen}{Research interests}}
        % & Your favorite topic, another topic, another topic, another topic, another topic \\
        % & \\
        
        % --- Section: Education ---
        
        \textcolor{OliveGreen}{Education} 
        & \href{https://www.nycu.edu.tw/nycu/en/index}{\textbf{National Yang Ming Chiao Tung University}} \hfill Hsinchu City, Taiwan \\ 
        & Applied Mathematics (\href{https://docs.google.com/spreadsheets/d/1hz9FwNdFio4EajAw5VN3lpa6QyxIE2GJ6FpHmMoSaaQ/edit?usp=sharing}{Grades}) \hfill Aug. 2022 -- Present \\
        & \qquad \  Exchange Program, \href{https://www.polytechnique.edu}{\'Ecole polytechnique}, France \hfill Sep. 2024 -- Jun. 2025 \\
        & \\
        
        & \textbf{National Hsinchu Senior High School} \hfill Hsinchu City, Taiwan \\
        & High School Degree, General Subjects \hfill Aug. 2019 -- Jun. 2022\\
        & \\
        
        % --- Section: Awards, scholarships, etc. ---
        % --- Note: section title is spread over two lines ---
        
        {\textcolor{OliveGreen}{Honors}} & \textbf{Outstanding Student Overseas Exchange Scholarship} \hfill Jun. 2024\\
        % & Supported by National Yang Ming Chiao Tung University and the Ministry of Education for the outbound exchange at \'Ecole polytechnique. \\
        & Supported by National Yang Ming Chiao Tung University and the Ministry of Education. \\
        & \\
        & \textbf{Mathematics Presidential Award} \hfill Sep. 2023\\
        & Awarded by the Department of Applied Mathematics, National Yang Ming Chiao Tung University for my study in mathematics in the second semester of the 2022 Academic Year.\\
        & \\
        & \textbf{Honor Student} \hfill May. 2023\\
        & Awarded by National Yang Ming Chiao Tung University for my study in the first semester of the 2022 Academic Year. \\
        & \\
        & \textbf{Mathematics Presidential Award} \hfill Feb. 2023\\
        & Awarded by the Department of Applied Mathematics, National Yang Ming Chiao Tung University for my study in mathematics in the first semester of the 2022 Academic Year.\\
        & \\
        & \textbf{Outstanding Performance Award} \hfill Jun. 2022\\
        & Awarded by the Hsinchu City Government for my overall performances during my course of study at National Hsinchu Senior High School.\\
        & \\
        
        % --- Section: Projects ---

        {\textcolor{OliveGreen}{Projects}} & \textbf{Study of Hitting Time and Probability} \hfill Jul. 2025 -- Feb. 2026\\
        & \textbf{\quad \quad \quad for Random Walks in One and Two Dimensions} \\
        & College Student Research Project, National Science and Technology Council\\
        & Studying the hitting and probability of random walks in one and two dimensions, focusing on their asymptotic behavior, under Prof. \href{https://scholar.nycu.edu.tw/en/persons/yuki-chino}{CHINO Yuki}. Funded by the National Science and Technology Council with project number 114-2813-C-A49-139-M.\\
        & \\
        

        & \textbf{Credit Card Fraud Detection Using Machine Learning} \hfill Feb. 2025 -- Jun. 2025\\
        & Group Project, \href{https://synapses.polytechnique.fr/catalogue/2024-2025/ue/47/CSC-2S004-EP-machine-learning?from=D12}{CSC\_2S004\_EP} - Machine Learning, École polytechnique\\
        & Developed a supervised machine learning pipeline to detect credit card fraud using real-world data with feature importance analysis and evaluation metrics. See this \href{https://github.com/eiken59/ml_project/blob/main/README.md}{repository}.\\
        & \\

        & \textbf{Chessbot Project: Cagnus} \hfill Nov. 2024 -- Jan. 2025\\
        & Group Project, \href{https://synapses.polytechnique.fr/catalogue/2024-2025/ue/32/CSC-2F001-EP-object-oriented-programming-in-c?from=D12}{CSC\_2S001\_EP} - Object-oriented Programming in C++, École polytechnique\\
        & Built a pure C++ chess engine without any non-standard libraries, achieving a final cross-match ranking of 9th out of 26 in the class. See this \href{https://github.com/jetzypetz/chess_bot/blob/main/docs/README.md}{repository}.\\
        & \\
        
        & \textbf{Before Finance} \hfill Jun. 2024 -- Jul. 2024\\
        & National Yang Ming Chiao Tung University Applied Mathematics \href{https://teshenglin.github.io/courses/2024_summer_research/}{Summer Research Internship}, Department of Applied Mathematics, National Yang Ming Chiao Tung University\\
        & Discussed \href{https://hackmd.io/@eiken-sc11/B1QcaW3B0}{topics} in mathematical finance, including gambler's ruin problem and matringale, under Prof. CHINO Yuki.\\
        & \\
        

        % --- Section: Work experience ---
        
        {\textcolor{OliveGreen}{Work}} & \textbf{Private Tutor} \hfill Sep. 2024 -- Present \\
        {\textcolor{OliveGreen}{Experience}} & Teaching and mentoring an eighth-grade student in mathematics (UK system), focusing on conceptual understanding and application; creating handouts with Typst.\\
        & \\
        
        & \textbf{Curriculum Material Developer} \hfill Mar. 2025 -- May. 2025 \\
        & \href{https://www.instagram.com/aijiatutoring/}{Aijia Tutoring}\\
        & Created a mathematics handout booklet for junior high second-year students, based on the Taiwan National Curriculum, as a paid private tutoring commission.\\
        & \\

        % & \textbf{Research Intern} \hfill Jun. 2024 -- Jul. 2024 \\
        % & National Yang Ming Chiao Tung University Applied Mathematics \href{https://teshenglin.github.io/courses/2024_summer_research/}{Summer Research Internship}, Department of Applied Mathematics, National Yang Ming Chiao Tung University\\
        % & Discussed \href{https://hackmd.io/@eiken-sc11/B1QcaW3B0}{topics} in mathematical finance, including gambler's ruin problem and matringale, under Prof. \href{https://scholar.nycu.edu.tw/en/persons/yuki-chino}{CHINO Yuki}.\\
        % & \\

        & \textbf{Teaching Assistant}  \hfill Sep. 2023 -- Dec. 2023\ \,\&\ \,Feb. 2024 -- Jun. 2024 \\
        & Department of Applied Mathematics, National Yang Ming Chiao Tung University\\
        & Conducted office hours and marked exams for \href{https://reurl.cc/Djp5jN}{Calculus A (I)} and \href{https://reurl.cc/RqoMez}{Calculus A (II)} under Prof. CHINO Yuki.\\
        & \\

        & \textbf{Academic Tutor} \hfill Oct. 2023 -- Nov. 2023\ \,\&\ \,Apr. 2024 -- May. 2024\\
        & Center of Teaching and Learning Development, National Yang Ming Chiao Tung University\\
        & Tutored international students in Calculus A (I) and Calculus A (II), conducting weekly sessions and creating \href{https://github.com/eiken59/2024_II_Tutor}{handouts} in \LaTeX.\\
        & \\

        & \textbf{Private Tutor} \hfill Apr. 2023 -- Jun. 2023 \\
        & Helped a high school student prepare for the Advanced Subjects Test in Mathematics A, focusing on problem-solving and exam strategies.\\
        & \\

        & \textbf{Part-Time Assistant} \hfill Sep. 2020 -- Jun. 2022 \\
        & Office of Student Affairs, National Hsinchu Senior High School\\
        & Built a student self-learning platform, created event posters and videos, managed assembly slides, and digitized documents.\\
        & \\

        & \textbf{Student Club Instructor} \hfill Sep. 2020 -- Jun. 2021 \\
        & Computer Software Design Club, National Hsinchu Senior High School\\
        & Taught coding in C++ (selection structure and number theory) and assisted club members during lectures.\\
        & \\

        % --- Section: Various skills (programming, software, languages, etc.) ---
        
        {\textcolor{OliveGreen}{Skills}} 
        & \textbf{Programming Languages}\\
        & C++ and Python.\\
        & \\

        & \textbf{Spoken Languages} \\
        & Mandarin (native), English (CEFR C1 certified), Japanese (JLPT N2 certified), and French (roughly CEFR B1 level).\\
        & \\

        % --- Section: Hobbies ---

        % \textcolor{OliveGreen}{Hobbies} & \textbf{Music} \\
        % & Piano, drums, and guitar. \\
        % & \\
        % & \textbf{Sports} \\
        % & Badminton.\\
        
        % --- End of CV! ---
        
    \end{longtable}
\end{center}

\end{document}
